---
title: "Summary"
author: "Sara Petchey"
date: "7/27/2017"
output:
  pdf_document: default
  html_document: default
---

# Organisation


- Always start RStudio by double clicking on the `TS_MOOC_DA.Rproj` file.

- Data dumps for each session should be in it's own folder in the `data` folder of the `project` folder.

- The data file loaded below, which contains all the csv files containing data, has to be previously made using the code `make_Rdata_file.R`.

- Put analyses scripts, such as these, in the `analyses` folder.

- Always use *relative paths*.


```{r, warnings=FALSE, message=FALSE}
# Some preliminaries
rm(list=ls())
library(tidyverse)
library(magrittr)
library(stringr)
```

# Load the data

Note that the data file loaded, which contains all the csv files containing data, has to be previously made using the code `make_Rdata_file.R`.

```{r}
## use the following if not using knitr
#load("data/biodiversity_1505727848128.Rdata")
## use the following if using knitr
load("../data/biodiversity_1505727848128.Rdata")
```



# Courses

Here we get the courses we have data for:
```{r}
courses
```
There is one course (note there might be an update somewhere).


# Course branches (= version)

Course branches (only one at the moment, I think, so not used in further analyses):
```{r}
course_branches
```
Only one course branch.


# On demand sesssions

On demand sessions:
```{r}
on_demand_sessions
```
Thirteen(?) on demand sessions.



# Learners in od sessions

Membership in each on demand session:
```{r}
on_demand_session_memberships
```
Note that some are duplicated as they come in and out of sessions.


Number of unique learners across all sessions:
```{r}
length(unique(on_demand_session_memberships$zurich_user_id))
```


Number of unique learners per session:
```{r}
num_learners_per_session <- on_demand_session_memberships %>%
  group_by(on_demand_session_id) %>%
  summarise(num_learners = length(unique(zurich_user_id))) %>%
  full_join(on_demand_sessions)
num_learners_per_session
```

Number of unique learners per session, totalled:
```{r}
sum(num_learners_per_session$num_learners, na.rm=T)
```
Some individual learners participated in multiple sessions.


Look at learners per session:
```{r}
qplot(x=on_demand_sessions_start_ts, y=num_learners,
      data=num_learners_per_session)
```


# Video watching patterns

Bring in course items:
```{r}
course_structure <- left_join(course_items, course_item_types)
course_structure <- full_join(course_structure, course_lessons)
course_structure <- full_join(course_structure, course_modules)
```


```{r}
course_progress <- full_join(course_progress, course_progress_state_types)
course_progress <- full_join(course_progress, course_structure)
```


Video lecture viewing behaviour (all od sessions combined at present):
```{r}
## get number of users starting / finishing a video lecture
rez1 <- course_progress %>% filter(course_item_type_category=="lecture") %>%
  group_by(course_lesson_order,
           course_lesson_name,
           course_module_order,
           course_module_name,
           course_progress_state_type_desc) %>%
  summarise(number=length(unique(zurich_user_id)))

ggplot(rez1, aes(x=course_lesson_order, y=number,
                 colour=course_progress_state_type_desc)) +
  facet_wrap(~course_module_order, nrow=1) +
  geom_point() + geom_line() +
  xlab("Lesson") +
  ylab("Number of learners") +
  ggtitle("My graph")
```


# Peer reviewer behaviour


```{r}
peer_review_part_free_responses_t <- left_join(peer_review_part_free_responses,
                                               peer_reviews)
peer_review_part_free_responses_t <- left_join(peer_review_part_free_responses_t,
                                               peer_assignments)

peer_review_part_free_responses_t <- left_join(peer_review_part_free_responses_t,
                                                peer_assignment_review_schema_parts)
peer_review_part_free_responses_t <- left_join(peer_review_part_free_responses_t,
                                                 course_branch_item_peer_assignments)
peer_review_part_free_responses_t <- left_join(peer_review_part_free_responses_t,
                                                 course_structure)

## Peer assignments
sort(unique(peer_review_part_free_responses_t$peer_assignment_id))
sort(unique(peer_review_part_free_responses_t$peer_assignment_base_id))
## the first peer review assignment has no free responses, only tick boxes

## check for duplicated responses
sum(duplicated(peer_review_part_free_responses_t$peer_review_part_free_response_text))
## There are duplicates, but I think they are people giving the same response to different questions, and different people giving same responses, e.g. Good.

sum(xtabs(~peer_assignment_id, peer_review_part_free_responses_t))

peer_review_part_free_responses_t %>%
  group_by(peer_assignment_base_id, course_module_order,
           course_module_name, peer_assignment_review_schema_part_id) %>%
  summarise(number=n()) %>%
  ungroup() %>%
  select(-contains("id")) %>%
  arrange(course_module_order)

peer_review_part_free_responses_t %>%
  group_by(peer_assignment_id, course_module_order,
           course_module_name, peer_assignment_review_schema_part_id) %>%
  summarise(number=n()) %>%
  ungroup() %>%
  select(-contains("id")) %>%
  arrange(course_module_order)


xxx <- distinct(select(peer_review_part_free_responses_t,
                peer_assignment_base_id,
                peer_assignment_review_schema_part_id,
                peer_assignment_review_schema_part_prompt,
                course_item_name,
                course_module_order,
                course_module_name,
                course_module_desc)) %>%
  arrange(course_module_order) %>%
  select(-contains("id"))
xxx

```

```{r}
peer_review_part_free_responses_t <- peer_review_part_free_responses_t %>%
  mutate(review_length = nchar(peer_review_part_free_response_text))

good <- filter(peer_review_part_free_responses_t, review_length==4) %>%
  select(peer_review_part_free_response_text) %>%
  distinct()

ggplot(peer_review_part_free_responses_t, aes(x=log10(review_length))) +
  geom_histogram()

ggplot(peer_review_part_free_responses_t,
       aes(x=peer_review_created_ts, y=log10(review_length))) +
  geom_point() +
  facet_wrap(~course_module_name)
  


```





